\documentclass{muratcan_cv}

\setname{Muhammad Alvi}{}
\setaddress{Toronto, Canada}
\setmobile{+1 647-705-3925}
\setmail{muhammadalvi24@gmail.com}
% \setcitizenship{Eldian Citizen}
\setlinkedinaccount{https://www.linkedin.com/in/muhammadalvi/} 
\setgithubaccount{https://github.com/muhammadalvi} 
\setthemecolor{MidnightBlue}

    
\begin{document}

%Create header
\headerview
\vspace{1ex} % white space
%
\section{Education}
    \datedexperience{Bachelor of Computing}{Sep 2017 - Apr 2022}
    \explanation{University of Guelph}{Guelph, ON}
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
     Containerized data classifier utilizing AWS ECS with the migration from AWS EC2 fleet lowering computing costs by 26\%
     
     \smallskip
     \coloredbullet\ %
     Containerized data classifier utilizing AWS ECS with the migration from AWS EC2 fleet lowering computing costs by 26\%}
%
\section{Skills}
    \newcommand{\skillone}{\createskill{Programming Languages}{Python \cpshalf Java \cpshalf C++ \cpshalf C \cpshalf C\# \cpshalf JavaScript \cpshalf MATLAB \cpshalf Simulink}}
    %
    \newcommand{\skilltwo}{\createskill{Technologies}{AWS BS/EC/EC2/ELB \cpshalf Azure AD \cpshalf Docker \cpshalf React.js \cpshalf Flask \cpshalf Redis \cpshalf Spring \cpshalf Android \cpshalf ROS}}
    %
    \createskills{\skillone, \skilltwo}
    \vspace{-3mm} % reduces whitespace!
    %
% 
\section{Experience}
    %
    \datedexperience{Amazon Web Services}{May 2018 - Mar 2021}
    \explanation{Software Engineer}{Toronto, CA}
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
     Containerized data classifier utilizing AWS ECS with the migration from AWS EC2 fleet lowering computing costs by 26\%
     
     \smallskip
     \coloredbullet\ %
     Containerized data classifier utilizing AWS ECS with the migration from AWS EC2 fleet lowering computing costs by 26\%
     
     \smallskip
     \coloredbullet\ %
     Containerized data classifier utilizing AWS ECS with the migration from AWS EC2 fleet lowering computing costs by 26\%
    
    \smallskip 
    \coloredbullet\ %
     Modeled and simulated a quadrotor's attitude and translational dynamics in MATLAB/Simulink to quantify the stability and performance improvements of the proposed control system.
     
     \smallskip
     \coloredbullet\ %
     Adapted and extended existing C++ code architectures to facilitate prototype implementation and performed hardware-in-the-loop simulations, using Gazebo/ROS for testing.
     
     \smallskip
     }
     %
     \datedexperience{Amazon Web Services}{Sep 2017 - Dec 2017} 
    \explanation{Software Engineer}{Vancouver, BC} 
    \explanationdetail{ 
    \smallskip 
    \coloredbullet\ %
     Extended foundational Python code that performs Monte Carlo simulations for the Very Specific Space Mission.
     
     \smallskip
     \coloredbullet\ %
     Coordinated with Senior Engineers in validating and improving models while supplying time-sensitive simulation data for Critical Design Reviews. 
     
     \smallskip
     \coloredbullet\ %
     Generated reports for the Very Specific Space Mission performance under varied initial conditions of the Specific system to ensure its reliability before launch. 
     
    %  \smallskip
    \bigskip
     }
     %
     \datedexperience{Scotiabank}{Sep 2019 - Dec 2020} 
    \explanation{Software Engineer}{Toronto, ON} 
    \explanationdetail{ 
    \smallskip 
    \coloredbullet\ %
     Extended foundational Python code that performs Monte Carlo simulations for the Very Specific Space Mission.
     
     \smallskip
     \coloredbullet\ %
     Coordinated with Senior Engineers in validating and improving models while supplying time-sensitive simulation data for Critical Design Reviews. 
     
     \smallskip
     \coloredbullet\ %
     Generated reports for the Very Specific Space Mission performance under varied initial conditions of the Specific system to ensure its reliability before launch. 
     
    %  \smallskip
    \bigskip
     } 
%
\section{Notable Projects}
     %
    \datedexperience{RandoSite.com}{Mar 2021 - Sep 2021}
    \explanation{Full Stack Developer}{San Francisco, CA} 
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
     Independently built an open-source web application that performs advanced Monte Carlo calculations for options trading, receiving praise from the trading community for its simplicity and accessibility. 
     
     
     \smallskip
     \coloredbullet\ %
     Front and back-end development using the React and Flask (Python) frameworks, respectively. These services were containerized using Docker Compose to enable scalability in the software architecture.
     
     \smallskip
     \coloredbullet\ %
     Integrated the Azure Active Directory B2C service for secure user authentication and convenient identity management. 
     
    \smallskip
     }
     %
    \datedexperience{RandoApp Android App}{Jan 2018 - Apr 2018}
    \explanation{Full Stack Developer}{San Francisco, CA} 
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
     Collaborated with a team in building an Android application for monitoring the health status of trees in San Francisco. The app would assist the city in its urban planning and sustainability goals. 
    
    \smallskip 
    \coloredbullet\ %
    Implemented the user authentication system using the Android SDK (Java). Google Maps was integrated into the app to enable geotagging of trees and updating their health status by users.
      
     \smallskip
     \coloredbullet\ %
    Test-driven development of all back-end endpoints using JUnit testing. The back-end was deployed on a Tomcat server.   
     
     \smallskip
     }
\end{document}
